Succinct representations for abstract interpretation

### 2011-10-31 papers/PLDI2012/implicitization.tex
modif remarque Matthieu

For each control point $p_i$, we compute a disjunctive invariant
$\bigvee_{1\leq j \leq m_i} X_{i,j}$. We denote by $n_i$ the number of
distinct paths starting at $p_i$.
To perform the analysis, one chooses an integer $\delta_i \in [1,m_i]$, and
a mapping function $\sigma_i: [1,m_i] \times [1,n_i] \mapsto [1,m_i]$.
\MM{C'est moi ou le $\tau_{i,k}$ ne correspond pas exactement à la
  notation du début ? Au début, $\tau_{i,k}$ est la transition de $i$
  à $k$, alors que là, on est dans le multigraphe donc il y a
  plusieurs arrêtes entre deux points. Si je comprends bien,
  $\tau_{i,k}$ est le $k$-ième chemin partant de $i$, c'est ça ?
  Je mettrais bien ``... and for the $k$-th path starting from $i$,
  denoted $\tau_{i,k}$, the image...'' si c'est bien ça. D'ailleurs,
  faut-il forcément parler de boucle ici ? La technique ne s'applique
  pas à des chemins quelconques ?}
  The $k$-th path starting fom $p_i$ is denoted $\tau_{i,k}$.
  The image of the $j$-th disjunct $X_{i,j}$ by the path $\tau_{i,k}$ is joined with 
  $X_{i,\sigma(j,k)}$.
Initially, the $\delta_i$-th abstract value contains the initial states of
$p_i$, and all other abstract values contain~$\emptyset$.

>>>>

For each control point $p_i$, we compute a disjunctive invariant
$\bigvee_{1\leq j \leq m_i} X_{i,j}$. We denote by $n_i$ the number of
distinct paths starting at $p_i$.
To perform the analysis, one chooses an integer $\delta_i \in [1,m_i]$, and
a mapping function $\sigma_i: [1,m_i] \times [1,n_i] \mapsto [1,m_i]$.
\MM{C'est moi ou le $\tau_{i,k}$ ne correspond pas exactement à la
  notation du début ? Au début, $\tau_{i,k}$ est la transition de $i$
  à $k$, alors que là, on est dans le multigraphe donc il y a
  plusieurs arrêtes entre deux points. Si je comprends bien,
  $\tau_{i,k}$ est le $k$-ième chemin partant de $i$, c'est ça ?
  Je mettrais bien ``... and for the $k$-th path starting from $i$,
  denoted $\tau_{i,k}$, the image...'' si c'est bien ça. D'ailleurs,
  faut-il forcément parler de boucle ici ? La technique ne s'applique
  pas à des chemins quelconques ?}
  \JH{J'ai corrige\dots}
  The $k$-th path starting fom $p_i$ is denoted $\tau_{i,k}$.
  The image of the $j$-th disjunct $X_{i,j}$ by the path $\tau_{i,k}$ is then
  joined with $X_{i,\sigma(j,k)}$.
Initially, the $\delta_i$-th abstract value contains the initial states of
$p_i$, and all other abstract values contain~$\emptyset$.
